### 2022-11-02 draft/draft.tex
fixed typo

\caption{\label{tab:hierarchy}Summary of an hierarchical or nested view of block momdels.}
\centering
\begin{tabular}[t]{l|l|l|l|l}
\hline
Model & Parameters & Dimension & Matrix Decomposition & Reduction to simpler model\\
\hline
SBM & $K (K-1) / 2$ & $K$ & $P = Z B Z^\top$ & \\
\hline
DCBM & $K (K-1) / 2 + n$ & $K$ & $P = (\Omega Z) B (\Omega Z)^\top$ & $\omega = e$\\
\hline
PABM & $n K$ & $K^2$ & $P = X \Pi X^\top$ & $\lambda_{ik} = \omega_i \sqrt{\theta_{z_i, k}}$\\
\hline
\end{tabular}
\end{table}

@@

\begin{example}
Recall the UK faculty network in \ref{ex:uk-faculty}. 
If we wish to analyze this as an SBM or DCBM under the GRDPG framework, we can take the ASE of the adjacency matrix and see whether the embedding vectors lie around point masses or rays. 
We assume that this model is assortative, so $p = K$ and $q = 0$ in constructing the ASE. 
Because the fourth community only contains two members, we omitted it from this analysis. 
Figure \ref{fig:ukfaculty-ase} suggests that the appropriate model here is the DCBM. 
$K$-means clustering on the normalized embedding vectors results in a community detection accuracy of 96.7\%.

>>>>

\caption{\label{tab:hierarchy}Summary of an hierarchical or nested view of block momdels.}
\centering
\begin{tabular}[t]{l|l|l|l|l}
\hline
Model & Parameters & $\mathrm{rank}(P)$ & Matrix Decomposition & Reduction to simpler model\\
\hline
SBM & $K (K-1) / 2$ & $K$ & $P = Z B Z^\top$ & \\
\hline
DCBM & $K (K-1) / 2 + n$ & $K$ & $P = (\Omega Z) B (\Omega Z)^\top$ & $\omega = e$\\
\hline
PABM & $n K$ & $K^2$ & $P = X \Pi X^\top$ & $\lambda_{ik} = \omega_i \sqrt{\theta_{z_i, k}}$\\
\hline
\end{tabular}
\end{table}

@@

\begin{example}
Recall the UK faculty network in \ref{ex:uk-faculty}. 
If we wish to analyze this as an SBM or DCBM under the GRDPG framework, we can take the ASE of the adjacency matrix and see whether the embedding vectors lie around point masses or rays. 
We assume that this model is assortative, so $p = K$ and $q = 0$ in constructing the ASE. 
Because the fourth community only contains two members, we omitted it from this analysis. 
Figure \ref{fig:ukfaculty-ase} suggests that the appropriate model here is the DCBM. 
$K$-means clustering on the normalized embedding vectors results in a community detection accuracy of 96.7\%, compared to an EM-based method which achieves 84\%.
